% LaTeX Curriculum Vitae Template
%
% Copyright (C) 2004-2009 Jason Blevins <jrblevin@sdf.lonestar.org>
% http://jblevins.org/projects/cv-template/
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely. No attribution is
% required in any resulting documents. I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.

\documentclass[letterpaper]{article}

\usepackage{hyperref}
\usepackage{geometry}

% Comment the following lines to use the default Computer Modern font
% instead of the Palatino font provided by the mathpazo package.
% Remove the 'osf' bit if you don't like the old style figures.
\usepackage[T1]{fontenc}
\usepackage[sc,osf]{mathpazo}

% Set your name here
\def\name{Bruce Collie}

% Replace this with a link to your CV if you like, or set it empty
% (as in \def\footerlink{}) to remove the link in the footer:
\def\footerlink{}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {computer science},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  body={6.5in, 8.5in},
  left=1.0in,
  top=1.25in
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\itshape\large}

% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets
%\renewenvironment{itemize}{
%  \begin{list}{}{
%    \setlength{\leftmargin}{1.5em}
%  }
%}{
%  \end{list}
%}

\begin{document}

% Place name at left
{\huge \name}

% Alternatively, print name centered and bold:
%\centerline{\huge \bf \name}

\vspace{0.25in}

\begin{minipage}{0.45\linewidth}
  Trinity Hall \\
  Trinity Lane \\
  Cambridge, UK \\
  CB2 1TJ
\end{minipage}
\begin{minipage}{0.45\linewidth}
  \begin{tabular}{ll}
    Phone: & +447591 461 843 \\
    Email: & \href{mailto:bsc28@cam.ac.uk}{\tt bsc28@cam.ac.uk} \\
    Skype: & \href{skype:bruce.collie}{bruce.collie}
  \end{tabular}
\end{minipage}

\section*{Education}

\begin{itemize}
    \item \textbf{University of Cambridge} \\
        \begin{tabular}{c}
            \emph{2013--2017}
        \end{tabular}
        \begin{itemize}
            \item \textbf{MEng} Computer Science \\
              \emph{In Progress}
            \item \textbf{BA Hons.} Computer Science \\
                \emph{Final Grade}: Class I
        \end{itemize}
\end{itemize}

\section*{Employment}

\begin{itemize}

    \item \textbf{Core Payments Intern} GoCardless \\
        \begin{tabular}{c|c}
            \emph{June--September 2016} & \emph{London, UK}
        \end{tabular}
        \begin{itemize}
          \item While at GoCardless I worked with the company's core payments
            team to improve and develop their banking infrastructure and
            processes.
          \item Projects I was responsible for included adding new features to
            internal risk and compliance tools, upgrading legacy code to allow
            for infrastructure changes, and designing auditing methods for
            changes to payment processes.
          \item I also spent time as the team's first responder, dealing with
            problems and queries about banking processes from across the
            company.
        \end{itemize}

    \item \textbf{Mobile Presales Intern} VNC Automotive \\
        \begin{tabular}{c|c}
            \emph{June--September 2015} & \emph{Cambridge, UK}
        \end{tabular}
        \begin{itemize}
            \item At RealVNC I was primarily responsible for prototyping an
                implementation of Apple's CarPlay in-car entertainment software.
            \item My role involved developing kernel drivers to support USB
                communication with the iPhone, as well as building the
                user-level CarPlay software itself.
            \item As well as CarPlay, I worked on several smaller projects
                related to the company's demonstration software that were of
                immediate value to my team.
        \end{itemize}

    
    \item \textbf{Mobile Development Intern} University of Cambridge, Mobile Systems Group \\
		\begin{tabular}{c|c}
            \emph{June 2014--April 2015} & \emph{Cambridge, UK}
		\end{tabular}
		\begin{itemize}

            \item I built a native iOS version of an existing Android
                application (\emph{EasyM}) for collecting survey response and
                sensor data from users who take part in research studies.

            \item As well as being of active use to researchers, my work also
                served to evaluate the potential of Swift and iOS as a platform
                for mobile sensing applications related to the work of the
                research group.

            \item My primary work was carried out during an internship from
                June--September 2014, with more work being carried out part time
                from then until April 2015. At the end of my internship period I
                presented on my work to a group of academics at a research group
                meeting.

		\end{itemize}
	
    \item \textbf{Lead iOS Developer} PenPalWorld \\
		\begin{tabular}{c|c}
			\emph{July 2013--April 2015} & \emph{Remote}
		\end{tabular}
		\begin{itemize}

            \item At PenPalWorld I created an iOS app for a an existing social
                networking site with over a million users. Creating the app also
                involved builing a custom web API to interface with the site's
                existing database.

            \item Throughout the project I worked closely with the owner
                and founder of PenPalWorld to produce a quality end product.

            \item On launch my app was used by approximately 150 unique users
                per day, and my responsibilities were expanded to include
                managing user satisfaction with the product.

\end{itemize}
	
    %\item \textbf{Assistant iOS Developer} Mostly Serious \\
%		\begin{tabular}{c|c}
%			\emph{July - August 2012} & \emph{Remote}
%		\end{tabular}
%		\begin{itemize}
%
 %           \item I worked remotely with Mostly Serious to assist their
  %              developers in the creation of a time tracking appliction for the
   %             iPhone.
%
%		\end{itemize}
	
    %\item \textbf{Bioengineering Intern} Heriot Watt University, Chemical Engineering Department \\
%		\begin{tabular}{c|c}
%			\emph{July - August 2012} & \emph{Edinburgh, UK}
%		\end{tabular}
%		\begin{itemize}
%
%            \item During my 5\textsuperscript{th} year at school I took part in
%                the Nuffield bursary scheme. I spent the summer working to
%                create an automated feedback system for controlling the growth
%                of yeast in a fermenter.
%
%		\end{itemize}
\end{itemize}

\section*{Other Projects}

\begin{itemize}

    \item \textbf{An Implementation of the $\pi$-Calculus} Part II Project \\
        \begin{tabular}{c|c}
            \emph{October 2015--May 2016} & \emph{Cambridge, UK}
        \end{tabular}
        \begin{itemize}
            \item In my final undergraduate year, my Part II project and
                dissertation involved the development of a programming language
                and runtime environment for the process algebra known as the
                $\pi$-Calculus.

            \item The project included a bytecode compiler for a language of my
                own design, as well as a full scheduling virtual machine to
                execute the bytecode.

            \item In undertaking this project, I gained strong experience in
                both the theory and practice of compiler implementation. Equally
                important was an understanding of the problems faced when
                building concurrent systems.

            \item The final project implementation and associated dissertation
                received a first-class mark.
        \end{itemize}

    \item \textbf{Webmaster} Trinity Hall June Event \\
        \begin{tabular}{c|c}
            \emph{October 2014--June 2015} & \emph{Cambridge, UK}
        \end{tabular}
        \begin{itemize}
            \item In my second year of university I took on the role of
                Webmaster for the Trinity Hall June Event 2015, the largest
                capacity event in Cambridge University's famous May Week (with
                2000 people attending the event).
            \item My responsibilities included designing a bespoke, responsive
                website design in conjunction with the event's graphic
                designers. The site is no longer online as it has been
                superseded by the site for 2016.
            \item I was also responsible for managing the use of the event's
                ticketing software. This involved both practical and technical
                skills---I ran a team of 6 people on the night of the event to
                control admission, as well as writing custom ticket generation
                and distribution software.
            \item The role required me to work effectively on a large team with
                a wide range of interests and responsibilities.
        \end{itemize}

\end{itemize}

\clearpage

\section*{Skills and Technologies}

    I am familiar with a wide range of programming languages and frameworks. My
    primary areas of expertise are: \\

	\begin{center}
		\renewcommand{\arraystretch}{2}
		\begin{tabular}{cp{10cm}}
            C & I have a good deal of experience writing code in C, including
            the implementation of kernel drivers and modifications to the Linux
            kernel. My skills surrounding systems programming are strong as a
            result of my time spent developing C. \\

            Scala & My final year project was implemented in Scala, and in doing
            so I have gained useful experience with strongly typed and
            functional languages, as well as elements of type theory. \\

            Python & I have experience with Python in a wide variety of
            contexts. My uses for it include analysis of experimental data,
            scripting / automation and development of web APIs using flask. \\

            iOS & I have been developing iOS applications both personally and
            professionally for over 3 years. My experience includes using both
            Objective-C and Swift. \\

            Java & I have used Java in a variety of contexts throughout my
            development career. These include writing significant programs for
            editing graphics, multithreaded and network programming.
        \end{tabular}
\end{center}

\bigskip

% Footer
\begin{center}
  \begin{footnotesize}
    Last updated: \today \\
    \href{\footerlink}{\texttt{\footerlink}}
  \end{footnotesize}
\end{center}

\end{document}
