%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Graduate Curriculum Vitae
% LaTeX Template
% Version 1.2 (3/28/15)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute 
% (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Modified by:
% Daniel L Marks <xleafr@gmail.com> 3/28/2015
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%-------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%-------------------------------------------------------------------------------

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% You can have multiple style options the legal options ones are:
%
%   centered:	the name and address are centered at the top of the page 
%				(default)
%
%   line:		the name is the left with a horizontal line then the address to
%				the right
%
%   overlapped:	the section titles overlap the body text (default)
%
%   margin:		the section titles are to the left of the body text
%		
%   11pt:		use 11 point fonts instead of 10 point fonts
%
%   12pt:		use 12 point fonts instead of 10 point fonts
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[margin]{res}  

% Default font is the helvetica postscript font
\usepackage{helvet}

\usepackage{hyperref}

% Increase text height
\textheight=700pt

\begin{document}

%-------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%-------------------------------------------------------------------------------
\name{Bruce Collie}

% Note that addresses can be used for other contact information:
% -phone numbers
% -email addresses
% -linked-in profile

\address{\href{mailto://bruce.collie@ed.ac.uk}{\texttt{bruce.collie@ed.ac.uk}}\\\href{http://baltoli.github.io}{\texttt{baltoli.github.io}}\\07591461843}
\address{104/3 Blackford Avenue\\Edinburgh\\EH9 3ES}

% Uncomment to add a third address
%\address{Address 3 line 1\\Address 3 line 2\\Address 3 line 3}
%-------------------------------------------------------------------------------

\begin{resume}

%-------------------------------------------------------------------------------
%	EDUCATION SECTION
%-------------------------------------------------------------------------------
\section{EDUCATION}
\textbf{University of Edinburgh}: CDT in Pervasive Parallelism \\
{\sl PhD} (2018--)\hfill In Progress
\\
{\sl MScR} (2017--18)\hfill
Distinction \\\\
\textbf{University of Cambridge}: Computer Science \\
{\sl MEng} (2016--17)\hfill Distinction \\
{\sl BA} (2013--16)\hfill $1^{\mathrm{st}}$ Class
%-------------------------------------------------------------------------------

%-------------------------------------------------------------------------------

%-------------------------------------------------------------------------------
%	EXPERIENCE SECTION
%-------------------------------------------------------------------------------
% Modify the format of each position
\begin{format}
\title{l}\employer{r}\\
\dates{l}\location{r}\\
\body\\
\end{format}
%-------------------------------------------------------------------------------

\section{EXPERIENCE}

\employer{University of Edinburgh}
\location{Edinburgh}
\dates{September 2017--}
\title{\textbf{PhD in Pervasive Parallelism}}
\begin{position}
My current employment is as a PhD student in the Compiler and Architecture
Design group at the University of Edinburgh. This position entails designing and
developing significant research applications, performing experiments and
authoring papers to showcase results. My work is primarily in C++, using the
LLVM compiler framework.
\end{position}

\employer{GoCardless}
\location{London}
\dates{June--September 2016}
\title{\textbf{Core Payments Developer}}
\begin{position}
At GoCardless I was a member of the group responsible for developing
public-facing backend web services, using Ruby on Rails. My responsibilities
included developing new libraries as part of the company's open-source work,
designing new features and modernising legacy code.
\end{position}

\employer{RealVNC}
\location{Cambridge}
\dates{June--September 2015}
\title{\textbf{Presales Developer}}
\begin{position}
During my internship at RealVNC I worked to develop a prototype implementation
of Apple's CarPlay entertainment system to run on the company's head unit
platform. This involved developing significant custom Linux kernel modules to interface with
the CarPlay USB protocol.
\end{position}

\employer{Mobile Systems Group}
\location{Cambridge}
\dates{June--September 2014}
\title{\textbf{Research iOS Developer}}
\begin{position}
As part of the Mobile Systems research group, I developed an iOS port of an
existing Android application for performing pyschological surveys. My work also
involved performing a feasibility study into the use of the Swift language for
the group in the future.
\end{position}

%-------------------------------------------------------------------------------
%	PROJECTS SECTION
%-------------------------------------------------------------------------------
\section{RESEARCH}

\par
\textbf{Program Synthesis}: I am interested in how program synthesis can be
applied to learn behavioural models of libraries and hardware devices, using
novel sources of information to efficiently navigate large solution search spaces.

\par
\textbf{Heterogenous Compilation}: My current research deals with new
compilation models for heterogenous architectures, investigating how compiler
developers and hardware vendors can cooperate to better optimise new and legacy
code for the next generation of devices.

\par
\textbf{TESLA}: I investigated the use of static model checking techniques in the TESLA runtime
temporal assertion system, demonstrating significant performance improvements on
real instrumented code by optimising statically provable assertions.


%-------------------------------------------------------------------------------
%	COMPUTER SKILLS SECTION
%-------------------------------------------------------------------------------
\section{SKILLS}

\textbf{Strong}: C++, C, LLVM, Python, Swift (iOS), Git

\textbf{Familiar}: JavaScript, Ruby, SQL

% \textbf{Languages}: C, C++, Java, ML, Perl, Bash, Assembly, SQL, \LaTeX.
% \\
% \textbf{Web Development}: HTML, CSS, JavaScript, PHP, Apache, IIS, ASP.NET.
% \\
% \textbf{Applications}: Vi/Vim, Eclipse, Visual Studio, Git, VMWare, VirtualBox, 
% MySQL, Oracle 11g.
% \\
% \textbf{Operating Systems}: 
% Unix, Linux, FreeBSD, Mac OSX, Windows, Android.
%-------------------------------------------------------------------------------

%-------------------------------------------------------------------------------
%	Interests
%-------------------------------------------------------------------------------
% \section{INTERESTS}
% Interest One, Interest Two, Interest Three, Interest Four, ...Et Cetera.
%-------------------------------------------------------------------------------
\end{resume}
\end{document}
