%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Plain Cover Letter
% LaTeX Template
% Version 1.0 (28/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute 
% http://www.rpi.edu/dept/arc/training/latex/resumes/
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt]{letter} % Default font size of the document, change to 10pt to fit more text

%\usepackage{newcent} % Default font is the New Century Schoolbook PostScript font 
\usepackage{helvet} % Uncomment this (while commenting the above line) to use the Helvetica font

% Margins
\topmargin=-1in % Moves the top of the document 1 inch above the default
\textheight=8.5in % Total height of the text on the page before text goes on to the next page, this can be increased in a longer letter
\oddsidemargin=-10pt % Position of the left margin, can be negative or positive if you want more or less room
\textwidth=6.5in % Total width of the text, increase this if the left margin was decreased and vice-versa

\let\raggedleft\raggedright % Pushes the date (at the top) to the left, comment this line to have the date on the right

\begin{document}

%----------------------------------------------------------------------------------------
%	ADDRESSEE SECTION
%----------------------------------------------------------------------------------------

\begin{letter}{ Galois, Inc. \\
Commonwealth Building \\
421 SW 6th Avenue \\
Portland, OR 97204} 

%----------------------------------------------------------------------------------------
%	YOUR NAME & ADDRESS SECTION
%----------------------------------------------------------------------------------------

\begin{center}
\large\bf Bruce Collie \\ % Your name
%\vspace{20pt} \hrule height 1pt % If you would like a horizontal line separating the name from the address, uncomment the line to the left of this text
1A Eachard Road \\ Cambridge, UK \\ CB3 0HZ \\ +447591461843
\end{center} 
\vfill

\signature{Bruce Collie} % Your name for the signature at the bottom

%----------------------------------------------------------------------------------------
%	LETTER CONTENT SECTION
%----------------------------------------------------------------------------------------

\opening{Dear Sir / Madam,} 

I am a student currently studying for a Masters degree at the University of
Cambridge in the UK. I will be graduating in the Summer of 2017, and will be
looking for a full-time position to begin after I do so. Having found out about
Galois through an online Haskell programming community, I became interested in
the opening for a Software Engineer / Researcher posted on the company jobs
page.

My primary interest in working at Galois comes from my desire to work with
Computer Science research in a practical context. I have a strong academic
record, including research experience in systems software and formal
verification (my r\'esum\'e provides further details). Additionally, I have
several years of practical software development experience in a number of
different contexts, working with both large and small teams to deliver effective
products---combined with my interest in Computer Science research, I believe
that I would be a good fit for a position at Galois. I am particularly
interested in the use of functional programming and formal methods to develop
verification tools for systems software.
 
I am currently located in the UK, but I hold full US citizenship and would be
willing to relocate to Portland if considered for this position. I look forward
to hearing from you regarding the next stage of the application process---I have
good availability for a Skype call (or similar) over the coming weeks.

\closing{Sincerely yours,}


%\encl{Curriculum vitae, employment form} % List your enclosed documents here, comment this out to get rid of the "encl:"

%----------------------------------------------------------------------------------------

\end{letter}

\end{document}
